A conditional permutation-based approach to test confounder and center effects in machine learning models

### 2021-10-23 supplement.tex
polished
Updates from Overleaf
patched

@@

\begin{equation}
    \mathbb{P}(\pi^{(j)} = \pi | \y,\yhat,\c) = \frac{q^n(\y_\pi | \c)}{\sum_{\pi' \in S_n} q^n(\y_{\pi'} | \c)}
    \label{eq-pperm}
\end{equation}

@@

\begin{figure}[H]
  \centering
  \fbox{
   \includegraphics[width=0.75\paperwidth]{fig/supplement/sim_ccc_full_normal_all_heatmap.pdf}}
  \caption{Heatmaps showing the positive rates of the 'full' confounder test, with normally distributed numerical simulated variables.}
  \label{fig:sim-ccc-full}
\end{figure}

\begin{figure}[H]
  \centering
  \fbox{
   \includegraphics[width=0.75\paperwidth]{fig/supplement/sim_ccb_partial_normal_all_heatmap.pdf}}
  \caption{Heatmaps showing the positive rates of the 'partial' confounder test, with normally distributed numeric $Y$ and $\hat{Y}$ and categorical $C$.}
  \label{fig:sim-ccb-partial}
\end{figure}

>>>>

\include{simulated/normality_and_linearity_violation}

@@

    $$\mathbb{P}(\pi^{(j)} = \pi | \y,\yhat,\c) = \frac{q^n(\y_\pi | \c)}{\sum_{\pi' \in S_n} q^n(\y_{\pi'} | \c)}$$

@@

\begin{figure}[H]
  \centering
  \fbox{
   \includegraphics[width=0.75\paperwidth]{fig/raw/sim_h1_ccc_partial_d10e0_sig_cpt_gam.pdf}}
  \caption{Heatmaps showing the positive rates of the 'partial' confounder test, with normal conditional distribution and sigmoid dependence.}
  \label{fig:sim-ccc-sig-partial}
\end{figure}
